Cross Validation Approaches for Penalized Cox Regression

### 2019-03-20 main.tex
Some edits to Section 4

\par In this section, we compared the performances of those cross validation methods when they are applied to data from real lung cancer study. \cite{shedden2008gene} conducted a large, retrospective study to validate prognostic gene expression signatures as predictors of overall survival in lung cancer patients, They performed gene expression profiling of \textit{442} non-small-cell lung cancer (NSCLC) patients. The data set contains gene expression measures from \textit{22,283} genes and basic clinical variables such as stage, age and gender. 236 death events were observed and about 50$\%$ of the patients are censored. The clinical variables stage, age and gender were known to have a larger prognostic impact, thus they were fitted in the model without penalization. Cross-validation was again used for the selection of the penalty term, which selects the gene expressions that are associated with patients' overall survival. The results of the analysis are also listed in Table 3.

>>>>

\par In this section, we apply the cross validation methods described in Section~\ref{Sec:methods} to data from a study of gene expression and survival in patients with lung cancer. \citet{shedden2008gene} conducted a large, retrospective study to validate prognostic gene expression signatures as predictors of overall survival in lung cancer patients.
They gathered expression profiles of \textit{22,283} genes for \textit{442} \note{is there some reason 442 is in italics? other numbers aren't} non-small-cell lung cancer (NSCLC) patients along with a number of clinical variables such as stage, age and gender. \note{Did you only adjust for stage, age, and gender, or did you adjust for smoking, etc., as well?  If not, maybe take out ``such as'', which implies that there are other variables you're not mentioning.} About 50\% of the patients died during the course of the study (236 events), with the rest censored. The clinical variables stage, age and gender were known to have a larger prognostic impact, thus they were fitted in the model without penalization. Cross-validation was again used for the selection of the penalty term, which selects the gene expressions that are associated with patients' overall survival. The results of the analysis are also listed in Table 3.
